---
title: Final Project 
author: "Author: Patrick Bautista" 
date: "'r format(Sys.time(), '%B %d, %Y @ %I:%M %p')`"
output: ioslides_presentation
---

```{r global_options, includes = FALSE}
knitr::opts_chunk$set(
  echo = FALSE,
  message = FALSE,
  warning = FALSE,
  comment = NA
)
```

## Packages Used

Tidyverse for data manipulation and plotting.

```{r, echo = TRUE}
library(tidyverse)
```


## Crytro Currency 

Cryto Currency is digital currency desugned to work as exchange currency through a computer network that is not dependent on any central authority, such as government bank, which avoids any upholds or maintenance from such bank.

Ethereum is a Crytro Currency that is decentralized, open-source block chain with sart contract functionality. Ethereum(Ether) is second only to Bitcoin in market capitalization.  


## Ethereum Cryptocurrency Historical Dataset

I gather my dataset from using KaggleDatasets, which is a data science company. Which allows users to explore and publish data sets, along with working with other data scientists machine learning engineers.

The dataset was last updated May 1, 2022, which is revalently recent just a few days off but it has change a bit since it's Crytocurrency.

**Variables in Dataset:**

* `Date`: Date of the ETH prices 
* `Open`: Opening Prices of ETH (Dollar equivalence)
* `High`: Highest price of ETH on the respective date (Dollar equivalence) 
* `Low`: Lowest price of ETH on the respective date (Dollar equivalence)
* `Close`: Closing price of ETH on the respective date (Dollar equivalence)
* `Volume`: Volume of ETH on the respective date (Dollar equivalence)


```{r}
data <- read_csv("Ethereum Historical Data.csv") 
```

##

```{r, fig.align = "center", fig.width = 7.5}
ggplot(data, aes(x = Open, y = Close))+ 
  geom_point() + 
  scale_x_discrete(labels = c("Open", "Close")) +
  scale_y_continuous(breaks = seq(from = 0, to = 5000, by = 625), limits = c(0, 5000)) +
  theme_minimal() + 
  theme( 
    axis.text.x = element_text(size = 13),
    axis.text.y = element_text(size = 11),
    axis.title.y = element_text(size = 15),
    panel.grid.major.x = element_blank(),
    legend.position = "none"
    ) + 
  # might need to add something here 
  labs(
    title = "Open & Close of Ethereum in dollars",
    subtitle = "Data includes dates of open & close", 
    caption = "Ethereum dollar equivalence is up to date",
    x =NULL ,
    y = "Amount of Dollar"
     )
```
  
  
```{r, fig.align = "center", fig.width = 7.5}
ggplot(data, aes(x = Low, y = High)) + 
  geom_line(linetype = "dotted", color = "green") + 
  geom_point()
```
  
  
```{r}
ggplot(data, aes( y = volume))+
  geom_bar() + 
  labs()
```
  
  

  
  
